Introductory statistics with `intRo`

### 2016-06-06 jcgs-paper-2016/paper.Rmd
Update response + references

Multiple software packages have recently been written in an attempt to spur student interest in introductory statistics and R programming. DataCamp's [@datacamp] courses are user-friendly ways to learning basic R programming and data analysis techniques. Swirl [@swirl] is a similar interactive tool to make learning R more fun by learning it within R itself. Project MOSAIC [@mosaic] has created a suite of tools to simplify the teaching of statistics in the form of an R package. The primary goal of DataCamp and Swirl is to teach R programming, rather than facilitate the learning of introductory statistics. Project MOSAIC's goal is to faciliate this learning, but using the package requires a knowledge of R programming that the introductory student may not have.

>>>>

Multiple software packages have recently been written in an attempt to spur interest in introductory statistics and R programming. DataCamp's [@datacamp] courses are user-friendly ways to learning basic R programming and data analysis techniques. Swirl [@swirl] is a similar interactive tool to make learning R more fun by learning it within R itself. Project MOSAIC [@mosaic] has created a suite of tools to simplify the teaching of statistics in the form of an R package. The primary goal of DataCamp and Swirl is to teach R programming, rather than facilitate the learning of introductory statistics. Project MOSAIC's goal is to faciliate this learning, but using the package requires a knowledge of R programming that the introductory student may not have. iNZight Lite [@inzight] also attempts to expose students to data analysis without requiring programming knowledge. While this tool has a lot of functionality and a very broad scope, it does not include reproducible R code, and therefore has less of a focus on spurring interest in coding for students. R Commander [@fox2005] and Deducer [@fellows2012] provides a graphical front-end to many statistical functions in R, but is not web-based and thus requires local installation and configuration.
